---
title: "&#32;"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
carob_path = "../../../carob/"

data_path = file.path(carob_path, "data/compiled")
data_path2 = file.path(carob_path, "data")
  
library(kableExtra)
library(terra)
library(geodata)
library(leaflet)

ff <- list.files(data_path, pattern=".csv$", full=TRUE)
ff <- ff[!grepl("_terms|_long", ff)]

## _metadata comes after _maize
sff <- gsub("_metadata", "_aaa", ff)
ff <- ff[order(sff)]

f <- grep(ff, pattern="_metadata.csv$", value=TRUE)

groups <- gsub("_metadata.csv$", "", basename(f))
groups <- gsub("^carob_", "", groups)
readcsv <- \(f) data.table::fread(f, sep=",", showProgress=FALSE)

d <- lapply(f, readcsv)
n1 <- sapply(d, nrow)
n2 <- sapply(d, \(i) sum(grepl("CC", i$license)))

f <- grep(ff, pattern="_metadata", invert=TRUE, value=TRUE)
fall <- grep(f, pattern="-cc", invert=TRUE, value=TRUE)
fcc <- grep(f, pattern="-cc", value=TRUE)

dd <- lapply(fall, readcsv)
nr1 <- sapply(dd, nrow)
ddcc <- lapply(fcc, readcsv)
nr2 <- sapply(ddcc, nrow)
grp2 <- gsub("-cc.csv$", "", basename(fcc))
grp2 <- gsub("^carob_", "", grp2)

d <- data.frame(Group=grp2, `CC-Records`=nr2, check.names=FALSE)

x <- data.frame(Group=groups, Datasets=n1, Records=nr1, `CC-Datasets`=n2, check.names=FALSE)
x <- merge(x, d, by="Group", all.x=TRUE)
x[is.na(x)] <- 0
xurl <- paste0("https://carob-data.org/reports/carob_",  x$Group, ".html")
x$Group <- kableExtra::cell_spec(x$Group, "html", link=xurl)

cdate <- format(Sys.time(), "%e %B %Y")
```

We aggregate agricultural research **data** into groups with similar variables. The table below shows the current groups and the number of original datasets and records in each group. We also show these numbers for the datasets that have a Creative Commons (CC) [license](licenses.html). As of `r  cdate`, we have processed `r sum(x$Datasets)` original [data sets](done.html) containing a total of `r format(sum(x$Records), big.mark=",")` records. 

<br>

```{r grouptable, echo=FALSE}
#kableExtra::kbl(x, "html") |> kable_classic(full_width = FALSE) |>
#   kable_styling(bootstrap_options = c("striped", "hover"))

kable(x, "html", escape = FALSE) |> kable_classic(full_width = FALSE) |>
  kable_styling(bootstrap_options = c("striped", "hover")) 
```

</br>

Here is a map with all locations for which we have at least one observation.

```{r map, echo=FALSE, fig.height=3.5}
w <- world(path=".")
geo <- do.call(rbind, lapply(1:length(dd), \(i) data.frame(Group=groups[i], dd[[i]][, c("country", "longitude", "latitude")]))) |> unique()
geo <- na.omit(geo)
v <- vect(geo, c("longitude", "latitude"), crs="+proj=longlat")

w <- project(w, "+proj=hatano")
g <- graticule(60, 30, "+proj=hatano")
v <- project(v, "+proj=hatano")

plot(g, col=gray(.95), background="azure", lwd=1.5, mar=c(.4, .2, 0, 0), lab.cex=.4)
plot(w, add=TRUE, col="light gray", border="white", lwd=1.5)
points(v, col="pink", cex=.5)
points(v, col="red", cex=.25)
lines(w, col="dark gray", lwd=1)
halo(-12000000, -6500000, paste("Carob locations\n  ", cdate), xpd=TRUE, cex=.6)
``` 
</br>
</br>


```{r reports, echo=FALSE}
p <- paste0("<a href=https://carob-data.org/reports/carob_", groups, ".html", ">", groups, "</a>")
p <- paste(p, collapse=", ")

#</br>Reports by group: `r p`</br>

```


